---
title: "TIF data download UHI and other variables"
author: "Pradnya Raut"
date: "2024-10-11"
output: html_document
---

```{r setup, include=FALSE}
gc()
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

# Intall & Load the libraries
```{r message=FALSE}

# Set CRAN mirror
options(repos = "http://cran.us.r-project.org")

# Include the libraries that are needed to be installed
libs <- c(
    "tidyverse", "sf", "geodata",
    "terra",  "dplyr", "utils", 
    "raster", "tibble", "readr"
)

#libs <- c(
#    "tidyverse", "sf", "geodata",
#    "terra", "classInt", "rayshader", "dplyr", "utils", 
#    "stars", "raster", "giscoR", "tidyterra", "plotly", "gridExtra", "e1071", 
#    "diptest", "xtable", "ggplot"
#)

installed_libs <- libs %in% rownames(
    installed.packages()
)

if (any(installed_libs == F)) {
    install.packages(
        libs[!installed_libs]
    )
}

invisible(lapply(
    libs,
    library,
    character.only = T
))

```


```{r}

```


# Unzip Cities Shapefile if not present in directory
```{r}
# Define file name and folder path
file_name <- "ne_10m_urban_areas_landscan.shp"
folder_path <- "../data/07_cities_shapefile"

# Check if the file exists in the folder
if (!file.exists(file.path(folder_path, file_name))) {
  # Unzip the file
  unzip(zipfile = file.path(folder_path, "data_EPSG_4326.zip"), exdir = folder_path)
}
```

# Load the cities shapefile
```{r}
file_name <- "ne_10m_urban_areas_landscan.shp"
folder_path <- "../data/07_cities_shapefile"

# Read the shapefile
world_city_map <- st_read(file.path(folder_path, file_name))
```
# City names stored in a list
```{r}
city_names <- unique(world_city_map$name_conve)
city_names_list <- as.list(city_names)

```

# Definition of getContinents() funciton
```{r}
getContinents <- function(city_polys, cont_polys) {
  # Assigns each city to a continent.
  names <- city_polys$name_conve
  continents <- cont_polys$NAME
  cont_list <- rep(NA, nrow(city_polys))
  for (i in 1:nrow(city_polys)) {
    poly <- city_polys$geometry[[i]]
    if (!is.null(poly)) {
      if (!st_is_valid(poly)) {
        poly <- st_buffer(poly, dist = 0)
      }
      center <- st_centroid(poly)
      min_dist <- 999999
      for (j in 1:nrow(cont_polys)) {
        cont_poly <- cont_polys$geometry[[j]]
        d <- st_distance(center, cont_poly)
        if (length(st_intersection(poly, cont_poly)) > 0) {
          cont_list[i] <- continents[j]
          break
        }
        if (d < min_dist) {
          min_dist <- d
          cont_list[i] <- continents[j]
        }
      }
    }
  }
  return(cont_list)
}
```

# Get Continents name for each city
```{r}
# this shape file is already on github. If not: 
# download the "label areas" from:
# url: https://www.naturalearthdata.com/downloads/50m-physical-vectors/50m-physical-labels/
# the downloaded zip file should be inside folder: '09_continents_shapefile'

# Define file name and folder path
file_name <- "ne_50m_geography_regions_polys.shp"
folder_path <- "../data/09_continents_shapefile"

# Check if the file exists in the folder
if (!file.exists(file.path(folder_path, file_name))) {
  # Unzip the file
  unzip(zipfile = file.path(folder_path, "ne_50m_geography_regions_polys.zip"), exdir = folder_path)
}

# Read the shapefile
continents_data <- st_read(file.path(folder_path, file_name))

options(timeout = 5)

# Filter data based on condition
continents_data <- continents_data[continents_data$FEATURECLA == 'Continent', ]

# Call the function
result <- getContinents(world_city_map, continents_data)

options(timeout = 5)

world_city_map$Continent <- result
```




## Open UHI and other Variable files

```{r UHI, echo=FALSE}
terraOptions(verbose=TRUE)
library(terra)
open_tif <- function(tif_file, asraster = FALSE){
  if (asraster == TRUE)
    outfl <- terra::rast(tif_file)
  else
    outfl <- stack(tif_file)
  #library(raster)
  #my_raster <- raster(tif_file)
  #crs(my_raster) <- "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"

return(outfl) #my_raster) # outfl)
}

ndviprocess <- FALSE
s_water_process <- FALSE  #TRUE

uhi <- open_tif("../data/10_raw_Other_variables/UHI_yearly_pixel_2018.tif") 

surfacewater_list <- list()
if (s_water_process){
  # surfacewater1 <- open_tif("../data/10_raw_Other_variables/SurfaceWater_2018_30m_30_0.tif", FALSE)
  # surfacewater2 <- open_tif("../data/10_raw_Other_variables/SurfaceWater_2018_30m_30_1.tif", FALSE)
  # surfacewater3 <- open_tif("../data/10_raw_Other_variables/SurfaceWater_2018_30m_30_2.tif", FALSE)
  # surfacewater4 <- open_tif("../data/10_raw_Other_variables/SurfaceWater_2018_30m_30_3.tif", FALSE)
  # surfacewater5 <- open_tif("../data/10_raw_Other_variables/SurfaceWater_2018_30m_30_4.tif", FALSE)
  # surfacewater6 <- open_tif("../data/10_raw_Other_variables/SurfaceWater_2018_30m_30_5.tif", FALSE) 
  # surfacewater_list = list(surfacewater0, surfacewater1, surfacewater2, surfacewater3,
  #                    surfacewater4, surfacewater5)
  sfiles <- list.files("../data/10_raw_Other_variables/", pattern = "/SurfaceWater_2018_30m_30_*.tif$", full.names = FALSE)
  surfacewater_list <- open_tif(sfiles)
  swatercsv = read_csv("../data/10_raw_Other_variables/City_surface.csv") #, header = TRUE)
  }

if (ndviprocess){
  ndvicsv = read_csv("../data/10_raw_Other_variables/City_NDVI_files.csv") #, header = TRUE)
  nfiles <- list.files("../data/10_raw_Other_variables/", pattern = "/Global_NDVI_*.tif$",
                       full.names = FALSE)
  ndvi_list <- open_tif(sfiles)

  #ndvi <- open_tif("../data/10_raw_Other_variables/MOD_NDVI_M_2018-03-01_rgb_3600x1800.tif") 

  #library(raster)
  #my_raster <- raster("path_to_your_file.tif")
  #crs(uhi) <- "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"
}

uhi
uhi_day <- uhi[["Daytime"]]
uhi_night <- uhi[["Nightime"]]
#uhi_combined <- uhi_day + uhi_night

uhi_day
uhi_night
#uhi_combined
#head(uhi_df)

#print(uhi)
#head(values(uhi))
#print(proj4string(uhi))
#print(extent(uhi))

#, b = 3,         
#plotRGB( uhi)  #, 3,2,1) #,
        #r = 3, g = 4, b = 3,
        #scale = 800,
        #stretch = "hist")

#ggplot() +
#  geom_raster(data = uhi_df,
#              aes(x = x, y = y, alpha = Daytime)) + 
#  coord_equal()
```

## Crop Cities from world map

```{r UHI raster processing, echo=FALSE}
library(tibble)
library(dplyr)
library(terra)
library(sf)
library(readr)
crop_city <- function(tif_raster, cty_nm){
  city_sf <- world_city_map %>%
    filter(name_conve %in% cty_nm)
  
  city_variable <- terra::crop(  tif_raster, city_sf)
  
    
  # crop city height from building_h object
  #city_variable <- terra::crop(
  #  tif_raster,
  #  #convert to terra friendly format
  #  terra::vect(city_sf), 
  #  # crop the inside
  #  snap = "in", 
  #  # remove everything except city_sf
  #  mask = T
  #)
  
  # Set a timeout of 5 seconds 
  #options(timeout = 15)
  
}
    
city_mean <- function(city_variable){  
  # terra::aggregate to reduce dim
  city_variable_agg <- city_variable |>
    terra::aggregate( fact = 3)
  return(city_variable_agg)
}

city_meanval <- function(city_variable ){
  mean_df <- colMeans(city_variable, na.rm = TRUE)
  totcol <- ncol(city_variable)
  print(totcol)
  meancolvalue <- mean_df[totcol][1] # colmn]  #Daytime]
  #meancolvalue <-0
  print(meancolvalue)
  print(mean_df)
  return(meancolvalue)
}
    
city_to_df <- function(city_variable, ncolmn){    
  # convert raster data to dataframe
  city_variable_df = as.data.frame(
    city_variable, 
    xy = T, 
    na.rm = T
  )
  head(city_variable_df)
  city_variable_df<- (city_variable_df) %>%
     filter( is.numeric(as.numeric(as.character(city_variable_df$ncolmn) )) )
  # Convert all values to numeric
  city_variable_df[] <- lapply(city_variable_df, function(x) as.numeric(as.character(x)))
  # Replace NA values with zero
  city_variable_df[is.na(city_variable_df)] <- 0
  return(city_variable_df)
}

#Save raster
save_raster<- function(city_variable, rastername){
  # Output Folder
  output_folder <- "../data/11_Output_R/city_rasters/"

  # Check if the output folder exists, if not, create it
  if (!file.exists(output_folder)) {
    dir.create(output_folder, recursive = TRUE)
  }

  # Specify the file path where we want to save the raster
  fl = paste(city_name,"_",rastername,".tif")
  print(rastername)
  output_file <- paste(output_folder, fl, sep = "" ) #city_name, sep = "")

  # Write the raster to a GeoTIFF file
  writeRaster(city_variable, filename = output_file, overwrite = TRUE)
  
  # Set a timeout of 5 seconds 
  #options(timeout = 5)
  
}
Process_surface_water<- function( city_name){
}



start.time <- Sys.time()
nextfive <-0
counter <- 0
steps <- 1 #300

ctystart <- (nextfive* steps)+1
ctyend <- ctystart+ (nextfive* steps) -1
n <- ctyend  # 600

# Create the dataframe
AllCityMeans <- tibble(
  city = character(),
  mean_uhi_daytime = numeric(),
  mean_uhi_Nighttime = numeric(),
  mean_uhi_DayNight  = numeric(),
  mean_surface_water  = numeric(),
  mean_ndvi = numeric()
)
meansurfacewater <-0
meanndvi <-0
print(AllCityMeans)


for (city_name in city_names_list) {
  if (counter< ctystart ){
    counter <- counter +1
    next
  }
  
  print(city_name)

  city_sf <- world_city_map %>%
    filter(name_conve %in% city_name)

  
  city_variable <- terra::crop(  uhi_day, city_sf)
  print(city_variable )
  

  
  city_df <- city_to_df(city_variable, 'daytime')
  head(city_df)
  meanDaytimeval <- city_meanval(city_df )

  city_night <- terra::crop(  uhi_night, city_sf)
  print(city_night )
  city_Night_df <- city_to_df(city_night, 'nighttime')
  head(city_Night_df)
  meanNighttime <- city_meanval(city_Night_df )
    
  city_daynight <- terra::crop(  uhi, city_sf)
  save_raster(city_daynight, "uhi") # save raster
  
  print(city_daynight )
  city_dayNight_df <- city_to_df(city_daynight, 'daynight')
  city_dayNight_df$daynight <- ( city_dayNight_df$Daytime + 
    city_dayNight_df$Nightime )
  head(city_Night_df)
  mean_day_night <- city_meanval( city_dayNight_df )  
  
  if (s_water_process){
    swfile = FALSE
    
    fls <- swatercsv[swatercsv$city == city_name, ]
    flscount <- nrow(fls)
    firstfl = TRUE
    for (i in 1:nrow(fls)){ #(surfacewater_raster in surfacewater_list)
      rst <- fls$SurfaceFile
      if (rst > 0){
        srast = concats('SurfaceWater_2018_30m_30_',as.character(rst-1))
      
        surfacewater_raster <- terra::rast[surfacewater_list[srast]]
        city_surfacewater <- terra::crop( surfacewater_raster, city_sf)
        flname = "surfacewater"
        if (flscount > 0)
          flname = "surfacewater_"+as.character(i)
        save_raster(city_surfacewater, flname ) # save raster
        df <- city_to_df(city_surfacewater, 'waterclass')
        if (firstfl){
          city_surfacewater_df <- df
          first <- FALSE }
        else
          city_surfacewater_df <- rbind(city_surfacewater_df, df)
        
        mean_SWATER <- city_meanval( city_surfacewater_df )  
        meansurfacewater <-0    
        if (swfile == TRUE)
          print(city_surfacewater )
          #city_surfacewater_df <- city_to_df(city_surfacewater, 'waterclass')
          #head(city_surfacewater)
          #meansurfacewater <- city_meanval(city_surfacewater_df)
      }
    }  
  }
  
  
  meanndvi <- 0
  # NDVI processing
  if (ndviprocess){
    fls <- ndvicsv[ndvicsv$city == city_name, ]
    flscount <- nrow(fls)
    firstfl = TRUE
    for (i in 1:nrow(fls)){ #(surfacewater_raster in surfacewater_list)
      rst <- fls$ndvi_file_name
      if (len(rst) > 0){
        nrast = concats('SurfaceWater_2018_30m_30_',as.character(rst-1))
      
        ndvi_raster <- terra::rast[rst]
        city_ndvi <- terra::crop( ndvi_raster, city_sf)
        flname = "surfacewater"
        if (flscount > 0)
          flname = "ndvi_"+as.character(i)
        save_raster(city_ndvi, flname ) # save raster
        df <- city_to_df(city_ndvi, 'waterclass')
        if (firstfl){
          city_ndvi_df <- df
          first <- FALSE }
        else
          city_ndvi_df <- rbind(city_ndvi_df, df)
    
    
        # city_ndvi <- terra::crop(  ndvi, city_sf)
        # save_raster(city_daynight, "ndvi") # save raster
        # 
        # print(city_daynight )
        # city_ndvi_df <- city_to_df(city_ndvi, 'ndvi')
        # head(city_ndvi_df)
        mean_ndvi <- city_meanval( city_ndvi_df )  
      }
    }
  }
  
  # Add a record to the dataframe
  AllCityMeans <- AllCityMeans %>%
  add_row(
    city = city_name,
    mean_uhi_daytime = meanDaytimeval,
    mean_uhi_Nighttime = meanNighttime,
    mean_uhi_DayNight  = mean_day_night,
    mean_surface_water = meansurfacewater,
    mean_ndvi = meanndvi
  )
  #print(AllCityMeans)
  print(AllCityMeans)
  nextfivefl <- as.character(nextfive)
  # Save the data frame to a CSV file
  write.csv(AllCityMeans, paste("../data/11_Output_R/Citywise Means",nextfivefl,".csv"), 
            row.names = TRUE,
            append=TRUE)
  #write.csv(AllCityMeans, "../data/11_Output_R/Citywise Means.csv", 
  #          row.names = !file.exists("../data/11_Output_R/Citywise Means.csv"),
  #          append=TRUE)


  
  counter <- counter + 1
  if (counter >= n) {
    break  # Break the loop when counter reaches n
  }  
#print(AllCityMeans)
# Save the data frame to a CSV file
#write.csv(AllCityMeans, "../data/10_raw_Other_variables/Citywise Means.csv", row.names = TRUE)
  

}
print(AllCityMeans)
end.time <- Sys.time()
time.taken <- end.time - start.time
time.taken
# Save the data frame to a CSV file
#write.csv(AllCityMeans, "../data/10_raw_Other_variables/Citywise Means.csv", row.names = TRUE)

unlink(tempdir(), recursive = TRUE) 
gc()

```

```{r - Not used now Open Files by chunk and convert to dataframe}
raster_to_df <- function(raster_path) {
  # Open the raster
  r <- raster(raster_path)
  
  # Create an empty dataframe to store results
  result_df <- data.frame()
  
  # Loop through rows in chunks
  for (row in 1:nrow(r)) {
    chunk <- getValuesBlock(r, row=row, nrows=100)
    chunk_df <- as.data.frame(chunk)
    chunk_df$row <- row  # Add row index
    
    # Append the chunk to the result dataframe
    result_df <- bind_rows(result_df, chunk_df)
  }
  
  return(result_df)
}

#raster_fl <- "../data/10_raw_Other_variables/UHI_Daytime_300_300_0.tif"
#df <- raster_to_df(raster_fl)
```


```{r ggplot}
#uhi_df <-df
#ggplot() +
#  geom_raster(data = uhi_df,
#              aes(x = x, y = y, alpha = Daytime)) + 
#  coord_equal()
```


```{r Uhi Daytime}
#uhiD <- open_tif("../data/10_raw_Other_variables/UHIg2pxAnnual_2018_Daytime_300_3000.tif")
#uhiD
#uhiD_df <- as.data.frame(uhiD, xy = TRUE)
#head(uhiD_df)
#plotRGB( uhiD)

#uhiN <- open_tif("../data/10_raw_Other_variables/UHIg2pxAnnual_2018_DayNightBandsum_300m_scale3003.tif")
#uhiN
#uhiN_df <- as.data.frame(uhiN, xy = TRUE)
#head(uhiN_df)

#plotRGB( uhiD)
#ggplot() +
#  geom_raster(data = uhiN_df,
#              aes(x = x, y = y, alpha = sum)) + 
#  coord_equal()

#uhiCombined <- uhiN # D  + uhiN
#uhiCombined
#uhiC_df <- as.data.frame(uhiCombined, xy = TRUE)
#ggplot() +
#  geom_raster(data = uhiC_df,
#              aes(x = x, y = y, alpha = layer)) + 
#  coord_equal()





```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
